Manuscript_Github_Pchabaudi_calculateTPM

### 2022-07-21 chapter3_results_bergheiPir/Pberghei_pir_samples_hclust-PCA-topGenes.Rmd
Start Pchabaudi R analysis

```{r read_tpm}
berghei_tpm <- read.csv('berghei_tpm.csv', 
                        row.names = 1)
```

>>>>

```{r read_tpm}
berghei_tpm <- read.csv('berghei_tpm.csv', 
                        row.names = 1)
expt_tpms <- lapply(na.omit(unique(str_extract(colnames(berghei_tpm), pattern = 'E[[:digit:]]{2}'))),
                    function(Enum){
                      df <- berghei_tpm[,str_subset(colnames(berghei_tpm), 
                                              pattern = paste0('Geneid|',Enum))]
                      colnames(df) <- str_remove( colnames(df) ,pattern = paste0(Enum, '_'))
                      list(experiment = Enum,
                           tpm = df)
                    })
names(expt_tpms) <- na.omit(unique(str_extract(colnames(berghei_tpm), pattern = 'E[[:digit:]]{2}')))
```

### 2022-07-21 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_calculateTPM.Rmd
Start Pchabaudi R analysis

library('readr')
library('dplyr')
library('tidyr')
library('ggplot2')
library('DESeq2')
library("pheatmap")
library("RColorBrewer")
library('data.table')
library('gridExtra')
library('tibble')
library('stringr')
library('kableExtra')
library('viridis')
library('corrplot')
library('reshape2')
library('circlize') # for circular plots and colours
library('cluster')    # clustering algorithms
library('factoextra') # clustering algorithms & visualization
library('ggfortify') # so ggplot understands prcomp objects
library('ape') # for phylogeny plotting
library('dendextend') # for dendrogram plotting
library('readxl') # for reading in Excel spreadsheets
library('plotly')
library('scales')
library('processx') # for downloading the plotly plots
library('cowplot')
library('ComplexHeatmap')
library('ggbiplot')
library('ggpattern')

>>>>

library('readr')
library('dplyr')
library('ggplot2')
# library("pheatmap")
library("RColorBrewer")
library('data.table')
library('gridExtra')
library('tibble')
library('stringr')
library('kableExtra')
library('viridis')
# library('corrplot')
# library('reshape2')
# library('circlize') # for circular plots and colours
# library('cluster')    # clustering algorithms
# library('factoextra') # clustering algorithms & visualization
# library('ggfortify') # so ggplot understands prcomp objects
# library('ape') # for phylogeny plotting
# library('dendextend') # for dendrogram plotting
# library('readxl') # for reading in Excel spreadsheets
# library('plotly')
# library('scales')
# library('processx') # for downloading the plotly plots
# library('cowplot')
# library('ComplexHeatmap')
# library('ggpattern')
